\begin{thebibliography}{a}
	\bibitem{1} \textsc{Economipedia}. \textit{Funciones de los bancos - Definici\'{o}n, qu\'{e} es y concepto}. Accedido 20 de mayo de 2021. \url{https://economipedia.com/definiciones/funciones-de-los-bancos.html}.
	\bibitem{2} \textsc{Ilyas, Sadaf, Sultan Zia, Zaib un Nisa, Umair Muneer Butt, y Sukumar Letchmunan}. \textit{Predicting the Future Transaction from Large an Imbalanced Banking Dataset}. IJACSA, 2020.
	\bibitem{3} \textsc{Technology partner for innovative companies}. \textit{Machine Learning in Banking - Opportunities, Risks, Use Cases}, 4 de febrero de 2021. \url{https://spd.group/machine-learning/machine-learning-in-banking/}.
	\bibitem{4} \textsc{Trivedi, Naresh, Sarita Simaiya, Dr Kumar, y Sanjeev Sharma}. \textit{An Efficient Credit Card Fraud Detection Model Based on Machine Learning Methods}. MATTER: International Journal of Science and Technology, 1 de enero de 2020.
	\bibitem{5} \textsc{Lima, Servio}. \textit{Deep Learning for Fraud Detection in the Banking Industry}. Human IST Institute, diciembre de 2018.
	\bibitem{6} \textsc{Boucher, \'{E}glantine}. \textit{Outlier Detection Methods Applied to Financial Fraud}, 2020.
	\bibitem{7} \textsc{Brownlee, Jason}. \textit{A Gentle Introduction to Imbalanced Classification}. Machine Learning Mastery (blog), 22 de diciembre de 2019. \url{https://machinelearningmastery.com/what-is-imbalanced-classification/}.
	\bibitem{8} \textit{Undersampling Algorithms for Imbalanced Classification}. Accedido 5 de julio de 2021. \url{https://machinelearningmastery.com/undersampling-algorithms-for-imbalanced-classification/}.
	\bibitem{9} \textsc{Brownlee, Jason}. \textit{Random Oversampling and Undersampling for Imbalanced Classification}. Machine Learning Mastery (blog), 14 de enero de 2020. \url{https://machinelearningmastery.com/random-oversampling-and-undersampling-for-imbalanced-classification/}.
	\bibitem{10} \textsc{Brownlee, Jason}. \textit{SMOTE for Imbalanced Classification with Python}, 17 de enero de 2021. \url{https://machinelearningmastery.com/smote-oversampling-for-imbalanced-classification/.}
	\bibitem{11} \textsc{Rui Nian}. \textit{Fixing Imbalanced Datasets: An Introduction to ADASYN (with code!)}. Medium. Accedido 5 de julio de 2021. \url{https://medium.com/@ruinian/an-introduction-to-adasyn-with-code-1383a5ece7aa}.
	\bibitem{12} \textsc{Sun, Bo, y Haiyan Chen}. \textit{A survey of k Nearest Neighbor Algorithms for Solving the Class Imbalanced Problem}, 17 de enero de 2021.
	\bibitem{13} \textit{Big Data}. Investopedia. Accedido 27 de mayo de 2021. \url{https://www.investopedia.com/terms/b/big-data.asp}.
	\bibitem{14} \textsc{Thudumu, Srikanth, Philip Branch, Jiong Jin, y Jugdutt (Jack) Singh}. \textit{A Comprehensive Survey of Anomaly Detection Techniques for High Dimensional Big Data}. Journal of Big Data 7, n.o 1 (diciembre de 2020): 42. \url{https://doi.org/10.1186/s40537-020-00320-x}.
	\bibitem{15} \textsc{Huang, Jian, Junyi Chai, y Stella Cho}. \textit{Deep learning in finance and banking: A literature review and clasification}, 2020. \url{https://doi.org/10.1186/s11782-020-00082-6}.
	\bibitem{16} \textsc{Nguyen, Thanh Thi, Hammad Tahir, Mohamed Abdelrazek, y Ali Babar}. \textit{Deep Learning Methods for Credit Card Fraud Detection}, s. f., 8.
	\bibitem{17} \textsc{Mohammed V, Rabat, Morocco, Ibtissam Benchaji, Samira Douzi, y Bouabid El Ouahidi}. \textit{Credit Card Fraud Detection Model Based on LSTM Recurrent Neural Networks}. Faculty of Sciences IPSS, University, Journal of Advances in Information Technology 12, n.o 2 (2021): 113-18. \url{https://doi.org/10.12720/jait.12.2.113-118}.
	\bibitem{18} \textsc{Nengcheng, Chen, Xiong Chang, Du Wenying, Wang Chao, Lin Xin, y Chen Zeqiang}. \textit{An Improved Genetic Algorithm Couplin a Back-Propagation Neural Network Model (IGA-BPNN) for Water-Level Predictions}, 30 de junio de 2019.
	\bibitem{19} \textit{Denoising Autoencoders with Keras, TensorFlow, and Deep Learning}, PyImageSearch, 24 de febrero de 2020. \url{https://www.pyimagesearch.com/2020/02/24/denoising-autoencoders-with-keras-tensorflow-and-deep-learning/}.
	\bibitem{20} \textsc{Brownlee, Jason}. \textit{Dropout Regularization in Deep Learning Models With Keras}. Machine Learning Mastery (blog), 19 de junio de 2016. \url{https://machinelearningmastery.com/dropout-regularization-deep-learning-models-keras/}.
	\bibitem{21} \textit{Clasificaci\'{o}n con datos desbalanceados | Aprende Machine Learning}. Accedido 7 de septiembre de 2021. \url{https://www.aprendemachinelearning.com/clasificacion-con-datos-desbalanceados/}.
	\bibitem{22} \textit{Keras: the Python deep learning API}. Accedido 3 de julio de 2021. \url{https://keras.io/}.
	\bibitem{23} \textit{Introduction to NumPy}. Accedido 3 de julio de 2021. \url{https://www.w3schools.com/python/numpy/numpy_intro.asp}.
	\bibitem{24} \textit{pandas PyPI}. Accedido 3 de julio de 2021. \url{https://pypi.org/project/pandas/}.
	\bibitem{25} \textit{scikit-learn: machine learning in Python - scikit-learn 0.24.2 documentation}. Accedido 3 de julio de 2021. \url{https://scikit-learn.org/stable/}.
	\bibitem{26} \textit{Matplotlib: Python plotting - Matplotlib 3.4.2 documentation}. Accedido 3 de julio de 2021. \url{https://matplotlib.org/}.
	\bibitem{27} \textit{imbalanced-learn documentation - Version 0.8.0}. Accedido 5 de julio de 2021. \url{https://imbalanced-learn.org/stable/}.
	\bibitem{28} \textit{PyCharm: the Python IDE for Professional Developers by JetBrains}. Accedido 5 de julio de 2021. \url{https://www.jetbrains.com/pycharm/}.
	\bibitem{29} \textsc{ITELLIGENT INFORMATION TECHNOLOGIES}. \textit{10 ventajas de la miner\'{i}a de datos}, 4 de agosto de 2016. \url{https://itelligent.es/es/10-ventajas-la-mineria-web/}.
	\bibitem{30} \textit{Sesion5\_Metodologias.pdf}. Accedido 3 de julio de 2021. \url{https://disi.unal.edu.co/~eleonguz/cursos/md/presentaciones/Sesion5\_Metodologias.pdf}.
	\bibitem{31} \textsc{Maimon, Oded, y Lior Rokach}, eds. Data Mining and Knowledge Discovery Handbook. Boston, MA: Springer US, 2010. \url{https://doi.org/10.1007/978-0-387-09823-4}.
	\bibitem{32} \textit{Redes neuronales con Python}. Accedido 13 de septiembre de 2021. \url{https://www.cienciadedatos.net/documentos/py35-redes-neuronales-python.html}.
	\bibitem{33} \textsc{Bushaev, Vitaly}. \textit{Adam - Latest Trends in Deep Learning Optimization.} Medium, 24 de octubre de 2018. \url{https://towardsdatascience.com/adam-latest-trends-in-deep-learning-optimization-6be9a291375c}.
\end{thebibliography}
